% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={305 Lecture 02 - The Nature of Logic},
  pdfauthor={Brian Weatherson},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\let\Tiny=\tiny

 \setbeamertemplate{navigation symbols}{} 

% \usetheme{Madrid}
 \usetheme[numbering=none, progressbar=foot]{metropolis}
 \usecolortheme{wolverine}
 \usepackage{color}
 \usepackage{MnSymbol}
% \usepackage{movie15}

\usepackage{amssymb}% http://ctan.org/pkg/amssymb
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\DeclareSymbolFont{symbolsC}{U}{txsyc}{m}{n}
\DeclareMathSymbol{\boxright}{\mathrel}{symbolsC}{128}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}


% \usepackage{tikz-qtree}
% \usepackage{markdown}
% \usepackage{prooftrees}
% \forestset{not line numbering, close with = x}
% Allow for easy commas inside trees
\renewcommand{\,}{\text{, }}


\usepackage{tabulary}

\usepackage{open-logic-config}

\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}

\AtBeginSection[]
{
\begin{frame}
	\Huge{\color{darkblue} \insertsection}
\end{frame}
}

\renewenvironment*{quote}	
	{\list{}{\rightmargin   \leftmargin} \item } 	
	{\endlist }

\definecolor{darkgreen}{rgb}{0,0.7,0}
\definecolor{darkblue}{rgb}{0,0,0.8}

\newcommand{\starttab}{\begin{center}
\vspace{6pt}
\begin{tabular}}

\newcommand{\stoptab}{\end{tabular}
\vspace{6pt}
\end{center}
\noindent}


\newcommand{\sif}{\rightarrow}
\newcommand{\siff}{\leftrightarrow}
\newcommand{\EF}{\end{frame}}


\newcommand{\TreeStart}[1]{
%\end{frame}
\begin{frame}
\begin{center}
\begin{tikzpicture}[scale=#1]
\tikzset{every tree node/.style={align=center,anchor=north}}
%\Tree
}

\newcommand{\TreeEnd}{
\end{tikzpicture}
%\end{center}
}

\newcommand{\DisplayArg}[2]{
\begin{enumerate}
{#1}
\end{enumerate}
\vspace{-6pt}
\hrulefill

%\hspace{14pt} #2
%{\addtolength{\leftskip}{14pt} #2}
\begin{quote}
{\normalfont #2}
\end{quote}
\vspace{12pt}
}

\newenvironment{ProofTree}[1][1]{
\begin{center}
\begin{tikzpicture}[scale=#1]
\tikzset{every tree node/.style={align=center,anchor=south}}
}
{
\end{tikzpicture}
\end{center}
}

\newcommand{\TreeFrame}[2]{
\begin{columns}[c]
\column{0.5\textwidth}
\begin{center}
\begin{prooftree}{}
#1
\end{prooftree}
\end{center}
\column{0.45\textwidth}
%\begin{markdown}
#2
%\end{markdown}
\end{columns}
}

\newcommand{\ScaledTreeFrame}[3]{
\begin{columns}[c]
\column{0.5\textwidth}
\begin{center}
\scalebox{#1}{
\begin{prooftree}{}
#2
\end{prooftree}
}
\end{center}
\column{0.45\textwidth}
%\begin{markdown}
#3
%\end{markdown}
\end{columns}
}

\usepackage[bb=boondox]{mathalfa}
\DeclareMathAlphabet{\mathbx}{U}{BOONDOX-ds}{m}{n}
\SetMathAlphabet{\mathbx}{bold}{U}{BOONDOX-ds}{b}{n}
\DeclareMathAlphabet{\mathbbx} {U}{BOONDOX-ds}{b}{n}

\RequirePackage{bussproofs}
\RequirePackage[tableaux]{prooftrees}

\newenvironment{oltableau}{\center\tableau{}} %wff format={anchor = base west}}}
       {\endtableau\endcenter}
       
\newcommand{\formula}[1]{$#1$}

\usepackage{tabulary}
\usepackage{booktabs}

\def\begincols{\begin{columns}}
\def\begincol{\begin{column}}
\def\endcol{\end{column}}
\def\endcols{\end{columns}}

\usepackage[italic]{mathastext}
\usepackage{nicefrac}

\definecolor{mygreen}{RGB}{0, 100, 0}
\definecolor{mypink2}{RGB}{219, 48, 122}
\definecolor{dodgerblue}{RGB}{30,144,255}

\def\True{\textcolor{dodgerblue}{\text{T}}}
\def\False{\textcolor{red}{\text{F}}}

\title{305 Lecture 02 - The Nature of Logic}
\author{Brian Weatherson}
\date{July 1, 2020}

\begin{document}
\frame{\titlepage}

\begin{frame}{Plan for This Lecture}
\protect\hypertarget{plan-for-this-lecture}{}

We're discussing the nature of arguments, and in particular, the role of
premises and conclusions.

\end{frame}

\begin{frame}{Associated Reading}
\protect\hypertarget{associated-reading}{}

Carnap book, chapter 1, section ``Arguments and Reasoning''.

\end{frame}

\begin{frame}{Arguments}
\protect\hypertarget{arguments}{}

Logic studies certain properties of arguments.

An argument, in the sense we're interested in, has two parts:

\begin{enumerate}
\tightlist
\item
  Premises
\item
  Conclusion
\end{enumerate}

\end{frame}

\begin{frame}{Example}
\protect\hypertarget{example}{}

\DisplayArg{ \item All kangaroos are wise. \item Skippy is a kangaroo. } { Skippy is wise. }

\end{frame}

\begin{frame}{Premises}
\protect\hypertarget{premises}{}

\DisplayArg{ \item All kangaroos are wise. \item Skippy is a kangaroo. } { Skippy is wise. }

The \textbf{premises} go above the line, and are numbered.

\end{frame}

\begin{frame}{Conclusion}
\protect\hypertarget{conclusion}{}

\DisplayArg{ \item All kangaroos are wise. \item Skippy is a kangaroo. } { Skippy is wise. }

The \textbf{conclusion} goes below the line, and is not numbered.

\end{frame}

\begin{frame}{The Premise Set}
\protect\hypertarget{the-premise-set}{}

\DisplayArg{ \item All kangaroos are wise. \item Skippy is a kangaroo. } { Skippy is wise. }

There can be zero, one or multiple premises. Formally, we'll say there
is a set of premises.

\end{frame}

\begin{frame}{Zero Premises}
\protect\hypertarget{zero-premises}{}

\hrulefill \begin{quote} {\normalfont All men are created equal.} \end{quote} \vspace{12pt}

\end{frame}

\begin{frame}{One Premise}
\protect\hypertarget{one-premise}{}

\DisplayArg{ \item The cinema is closed. } { We shouldn't go to the cinema. }

\end{frame}

\begin{frame}{Conclusion}
\protect\hypertarget{conclusion-1}{}

\DisplayArg{ \item All kangaroos are wise. \item Skippy is a kangaroo. } { Skippy is wise. }

But we don't allow this flexibility to conclusions; arguments have a
single conclusion.

\end{frame}

\begin{frame}{Chained Arguments}
\protect\hypertarget{chained-arguments}{}

\begin{itemize}
\tightlist
\item
  Sometimes a conclusion of one argument will go to be a premise in
  another argument.
\item
  But any given argument aims to prove just one thing.
\end{itemize}

\end{frame}

\begin{frame}{Representation}
\protect\hypertarget{representation}{}

\DisplayArg{ \item All kangaroos are wise. \item Skippy is a kangaroo. } { Skippy is wise. }

When I write arguments like this, I'm merely presenting them, not
asserting that they have any nice features.

\end{frame}

\begin{frame}{Virtues of Arguments}
\protect\hypertarget{virtues-of-arguments}{}

What are some virtues of arguments that you can think of? What makes for
a good argument?

\end{frame}

\begin{frame}{Virtues of Arguments}
\protect\hypertarget{virtues-of-arguments-1}{}

\begin{itemize}[<+->]
\tightlist
\item
  Premises are true.
\item
  Premises are known.
\item
  Premises are accepted in debate.
\item
  Premises are evidence for the conclusion.
\item
  Premises guarantee the truth of the conclusion.
\end{itemize}

\end{frame}

\begin{frame}{Logic}
\protect\hypertarget{logic}{}

To a first approximation, logic is about the last of these virtues.

\begin{itemize}
\tightlist
\item
  Does the truth of a set of premises \textbf{guarantee} the truth of
  the conclusion?
\end{itemize}

\end{frame}

\begin{frame}{Structure}
\protect\hypertarget{structure}{}

Logic isn't just about guarantees though. It's about a special kind of
guarantee, one that holds in virtue of the structure of the premises and
conclusion.

\end{frame}

\begin{frame}{Non-Structural Guarantee}
\protect\hypertarget{non-structural-guarantee}{}

Compare the Skippy argument with this one.

\DisplayArg{ \item Today is Wednesday. } { Tomorrow is Thursday. }

The premise guarantees the truth of the conclusion, but it does so in
virtue of meanings of `Wednesday' and `Thursday', not structural
features.

\end{frame}

\begin{frame}{Structure and Substitution}
\protect\hypertarget{structure-and-substitution}{}

When the structure of the argument does the guaranteeing, the guarantee
would persist through some substitutions.

\DisplayArg{ \item All kangaroos are wise. \item Skippy is a kangaroo. } { Skippy is wise. }

\end{frame}

\begin{frame}{Structure and Substitution}
\protect\hypertarget{structure-and-substitution-1}{}

When the structure of the argument does the guaranteeing, the guarantee
would persist through some substitutions.

\DisplayArg{ \item All kangaroos are wise. \item Lucky is a kangaroo. } { Lucky is wise. }

\end{frame}

\begin{frame}{Structure and Substitution}
\protect\hypertarget{structure-and-substitution-2}{}

When the structure of the argument does the guaranteeing, the guarantee
would persist through some substitutions.

\DisplayArg{ \item All koalas are wise. \item Lucky is a koala. } { Lucky is wise. }

\end{frame}

\begin{frame}{Structure and Substitution}
\protect\hypertarget{structure-and-substitution-3}{}

When the structure of the argument does the guaranteeing, the guarantee
would persist through some substitutions.

\DisplayArg{ \item All koalas are dishonest. \item Lucky is a koala. } { Lucky is dishonest. }

\end{frame}

\begin{frame}{Terminology}
\protect\hypertarget{terminology}{}

\begin{itemize}
\tightlist
\item
  We'll say an argument is \textbf{valid} just in case the truth of the
  premises guarantees the truth of the conclusion.
\item
  We'll say an argument is \textbf{sound} just in case it is valid and
  has true premises.
\item
  We won't have much interest here in soundness; just in validity.
\end{itemize}

\end{frame}

\begin{frame}{Validity}
\protect\hypertarget{validity}{}

Here are some equivalent ways to define validity.

\begin{itemize}
\tightlist
\item
  An argument is valid if necessarily, when the premises are true, the
  conclusion is too.
\item
  An argument is valid if it is impossible for the premises to be true
  and the conclusion to not be true.
\end{itemize}

We'll use that last formulation a lot.

\end{frame}

\begin{frame}{For Next Time}
\protect\hypertarget{for-next-time}{}

We'll look at the most fundamental kind of logic: propositional logic.

\end{frame}

\end{document}
